Automated Residual Plot Assessment with the R Package autovi and Shiny App autovi.web

### 2024-11-25 autovi_paper.qmd
add a section about vss

@@

### Numerical Summary {#sec-autovi-numerical}

@@

### Visual Summary {#sec-autovi-visual}

@@

## Modularized Infrastructure {#sec-autovi-infrastructure}

@@

# Resources and Supplementary Material

>>>>

# What is visual signal strength? {#sec-vss-desc}

**Visual signal strength** (VSS) refers to how prominently a specific set of visual patterns appears in an image. In the context of regression model diagnostics, it describes the clarity of visual patterns on a diagnostic plot that may indicate model violations. This concept can be categorized as weak, moderate, or strong. However, in our study, we treat it as a continuous positive real variable. Importantly, its interpretation depends on how it is linked to a function of the data or the underlying data generating process. Consequently, the meaning of visual signal strength varies across different model classes and even within the same model, depending on the chosen function.

In @li2024automated, visual signal strength was defined as an estimate of a distance measure that quantifies the disparity between the residual distribution of a fitted classical normal linear regression model and a reference distribution. This measure is based on the Kullback-Leibler (KL) divergence:

\begin{equation*} \label{eq:kl-0}
D = \log\left(1 + D_{KL}\right),
\end{equation*}

where $D_{KL}$ is given by:

\begin{equation*} \label{eq:kl-1}
D_{KL} = \int_{\mathbb{R}^{n}}\log\frac{p(\boldsymbol{e})}{q(\boldsymbol{e})}p(\boldsymbol{e})d\boldsymbol{e},
\end{equation*}

Here, $p(.)$ and $q(.)$ are the probability density functions of the reference residual distribution $P$ and the true residual distribution $Q$, respectively.

This distance measure requires knowledge of the true residuals' data generating process, which is typically unknown. Therefore, it must be estimated. To address this, a computer vision model was trained to perform the estimation.

@@

### Numerical summary {#sec-autovi-numerical}

@@

### Visual summary {#sec-autovi-visual}

@@

## Modularized infrastructure {#sec-autovi-infrastructure}

@@

# Resources and supplementary material

### 2024-11-25 autovi_paper.tex
add a section about vss

@@

\subsubsection{Numerical Summary}\label{sec-autovi-numerical}

@@

\subsubsection{Visual Summary}\label{sec-autovi-visual}

@@

\subsection{Modularized Infrastructure}\label{sec-autovi-infrastructure}

@@

\section{Resources and Supplementary
Material}\label{resources-and-supplementary-material}

>>>>

\section{What is visual signal strength?}\label{sec-vss-desc}

\textbf{Visual signal strength} (VSS) refers to how prominently a
specific set of visual patterns appears in an image. In the context of
regression model diagnostics, it describes the clarity of visual
patterns on a diagnostic plot that may indicate model violations. This
concept can be categorized as weak, moderate, or strong. However, in our
study, we treat it as a continuous positive real variable. Importantly,
its interpretation depends on how it is linked to a function of the data
or the underlying data generating process. Consequently, the meaning of
visual signal strength varies across different model classes and even
within the same model, depending on the chosen function.

In \citet{li2024automated}, visual signal strength was defined as an
estimate of a distance measure that quantifies the disparity between the
residual distribution of a fitted classical normal linear regression
model and a reference distribution. This measure is based on the
Kullback-Leibler (KL) divergence:

\begin{equation*} \label{eq:kl-0}
D = \log\left(1 + D_{KL}\right),
\end{equation*}

where \(D_{KL}\) is given by:

\begin{equation*} \label{eq:kl-1}
D_{KL} = \int_{\mathbb{R}^{n}}\log\frac{p(\boldsymbol{e})}{q(\boldsymbol{e})}p(\boldsymbol{e})d\boldsymbol{e},
\end{equation*}

Here, \(p(.)\) and \(q(.)\) are the probability density functions of the
reference residual distribution \(P\) and the true residual distribution
\(Q\), respectively.

This distance measure requires knowledge of the true residuals' data
generating process, which is typically unknown. Therefore, it must be
estimated. To address this, a computer vision model was trained to
perform the estimation.

@@

\subsubsection{Numerical summary}\label{sec-autovi-numerical}

@@

\subsubsection{Visual summary}\label{sec-autovi-visual}

@@

\subsection{Modularized infrastructure}\label{sec-autovi-infrastructure}

@@

\section{Resources and supplementary
material}\label{resources-and-supplementary-material}
